### 2014-02-28 paper/retrofit.tex
todos for me

Finally, in Figure~\ref{fig:embedding},
we provide all of the rules responsible for actually carrying out the embedding.
The most important feature of this embedding is that every thread maintains its own
copy of the target language global state and evaluation context, thus
enforcing isolation between various threads.  In more detail:

@@

\begin{code}
ix1, ix2 <= brecv . ie @=
tab tab tab IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
\end{code}

>>>>

\Red{TODO[ds]:
  - move the async recv to text and out of the figure
  - clarify discussion on exceptions
  - fix the toLabled
  - add threadId to ruls
}
Finally, in Figure~\ref{fig:embedding},
we provide all of the rules responsible for actually carrying out the embedding.
The most important feature of this embedding is that every thread maintains its own
copy of the target language global state and evaluation context, thus
enforcing isolation between various threads.  In more detail:

@@

\begin{code}
ix1, ix2 <= brecv . ie @=
tab tab tab (IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx))
conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
\end{code}
